\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-28 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Minor typo

	Figure \ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.  In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast.

>>>>

	Figure \ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{\bm{y}}$ at the right-angled vertex.  In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast.
